---
title: "HW1_Wei(Will)Jiang"
author: "Wei (Will) Jiang"
date: "10/28/2021"
output: html_document
---

# Set up
```{r}
library(data.table)
all_edges = fread("C:/Users/Will Jiang/Desktop/Emory Desktop/Network/HW/HW1/social_and_task_network.csv", head = TRUE)
library(igraph)
```

# Q1: Centrality

## Q1(A): calculate centrality
```{r,warning=FALSE}
nonzero_edges <- all_edges[social_tie > 0 | task_tie > 0] #removing edges with both social and task weight = 0
all_network <- graph.data.frame(nonzero_edges,directed = FALSE) #no direction needed

#social ties
social <- delete.edges(all_network, E(all_network)[E(all_network)$social_tie==0]) #left only with social ties
social <- delete.vertices(social, V(social)[degree(social)==0]) #remove the social isolates

#calculate different centralities
social_indegree <- degree(social, mode='in',normalized = TRUE)
social_outdegree <- degree(social, mode='out',normalized = TRUE)
social_closeness <- closeness(social, weights=E(social)$social_tie, normalized = TRUE)
social_betweenness <- betweenness(social, weights=E(social)$social_tie, normalized = TRUE)
social_pagerank <- page_rank(social,weights=E(social)$social_tie)

#show centralities together
social_centralities <- cbind(social_indegree,social_outdegree,social_closeness,social_betweenness,social_pagerank$vector)
colnames(social_centralities) <- c('indegree','outdegree','closeness','betweenness','page rank')
social_centralities
```
```{r,echo=FALSE,warning=FALSE}
#task ties
task <- delete.edges(all_network, E(all_network)[E(all_network)$task_tie==0]) #left only with task ties
task <- delete.vertices(task, V(task)[degree(task)==0]) #remove the task isolates

#calculate different centralities
task_indegree <- degree(task, mode='in',normalized = TRUE)
task_outdegree <- degree(task, mode='out',normalized = TRUE)
task_closeness <- closeness(task, weights=E(task)$task_tie, normalized = TRUE)
task_betweenness <- betweenness(task, weights=E(task)$task_tie, normalized = TRUE)
task_pagerank <- page_rank(task,weights=E(task)$task_tie)

#show centralities together
task_centralities <- cbind(task_indegree,task_outdegree,task_closeness,task_betweenness,task_pagerank$vector)
colnames(task_centralities) <- c('indegree','outdegree','closeness','betweenness','page rank')
task_centralities
```

## Q1(B): correlations among centrailities
```{r}
rownames(social_centralities)
rownames(task_centralities)
both_cen <- Reduce(intersect,list(rownames(social_centralities),rownames(task_centralities))) #get people in both social and task centralities
social_centralities_sub <- social_centralities[both_cen,]
task_centralities_sub <- task_centralities[both_cen,]
cor(social_centralities_sub, task_centralities_sub) #calculate correlation matrix
```
Comment:
(1) social network betweenness centrality is closely correlated with task network indegree, outdegree, betweenness and page rank centralities. For instance, people who have high betweenness in social network may also have high indegree, outdegree, betweenness and page rank in the task network. This may because people with high betweenness is a bridge of unrelated people, they tend to find this brokerage person for social and task information and cooperation.
(2) social network indegree and outdegree centrality is also correlated with indegree and outdegree of task network.
(3) social network closeness centrality is correlated with that of task network.People who tend to be the center of social network may also have high posibility to be the task center since they may communicate with each other about courses when they hanging out together or after class.

# Q2: Strong Triadic Closure
Assumption: if there is at least a strong tie between two nodes (no matter it's social or task network), then they have strong tie.

## Q2(A) plot inviolation Strong Triadic Closure
```{r}
social_weak <- which(E(all_network)$social_tie <= mean(E(all_network)$social_tie))
task_weak <- which(E(all_network)$task_tie <= mean(E(all_network)$task_tie))
both_weak <- Reduce(intersect,list(social_weak,task_weak)) #select edge if both social tie and task tie are weak
strong_network <- delete.edges(all_network,both_weak) #select edge as long as strong ties exist
plot.igraph(strong_network,vertex.label=NA,layout=layout.fruchterman.reingold,vertex.label.color="black",edge.color="black",vertex.size = 12, edge.arrow.size=.3,edge.curved=FALSE)
```
Comment: as we can find in the plot, some nodes in the network do not satisfy the Strong Triadic Closure.

## Q2(B): calculate number of inviolation Strong Triadic Closure
```{r}
#generate a strong matrix with complete rows and columns (1:22)
strong_network <- simplify(strong_network) #delete duplicates and loops
strong_network_matrix <- as_adjacency_matrix(strong_network) #get matrix with only strong ties between nodes
strong_network_matrix <- rbind(strong_network_matrix[1:2,],c(rep(0,21)),strong_network_matrix[-(1:2),]) #add a new row with all 0
rownames(strong_network_matrix) <- seq(1,22) #rename the row names
strong_network_matrix <- cbind(strong_network_matrix[,1:2],c(rep(0,22)),strong_network_matrix[,-(1:2)]) #add a new row with all 0
colnames(strong_network_matrix) <- seq(1,22) #rename the column names

#for every node: get nodes who are connected with it by strong ties, and generate the possible combinations of those nodes
more_than_one_strong <- which(apply(strong_network_matrix,1,sum) >= 2) #select only rows  with >= 2 strong ties
all_combn <- matrix(ncol=2)
for (i in more_than_one_strong) {
  new_combn <- t(combn(which(strong_network_matrix[i,]==1),2))
  all_combn <- rbind(all_combn,new_combn)
}
colnames(all_combn) <- c('y1','y2')

#according to Strong Triadic Closure, those nodes generated above should have ties, so I compare them with all relationships, if FALSE then it violates the rule
all_relations <- as.matrix(nonzero_edges[,1:2])
all_relations <- transform(all_relations,all_relations_1=interaction(ego,alter,sep='_')) 
all_combn <- transform(all_combn,all_combn=interaction(y1,y2,sep='_'))

sum(all_relations$all_relations %in% all_combn$all_combn == FALSE)/2 #count the number of inviolation
```
Comments: There are 28 ties that are inviolation of Strong Triadic Closure.

# Q3: Edge-level Betweenness

## Q3(A): Edge-level betweenness
```{r}
social_edge_betweenness <- edge_betweenness(social,e = E(social),weights=E(social)$social_tie)
task_edge_betweenness <- edge_betweenness(task,e = E(task),weights=E(task)$task_tie)
```

## Q3(B): Strong tie or not
```{r}
social_strong_edge_judge <- E(social)$social_tie > mean(E(social)$social_tie) #boolean, edge is strong(1) or weak(0)
cbind(social_edge_betweenness,social_strong_edge_judge) #see edge betweenness and whether they are strong or weak

task_strong_edge_judge <- E(task)$task_tie > mean(E(task)$task_tie) #boolean, edge is strong(1) or weak(0)
cbind(task_edge_betweenness,task_strong_edge_judge) #see edge betweenness and whether they are strong or weak
```
Comment: From the combined result we can find that edges with high betweenness tend to be weak ties. This result makes sense given the shape of the networks.

# Q4: Pairs of No Walks

## (1) Method 1
Use distances() to calculate there are 38 pairs of nodes do not have walks between one another.
```{r}
all_network_dis <- distances(all_network)
sum(is.infinite(all_network_dis))/2
```

## (2) Method 2
Idea: Calculate number of 1-21 walks between nodes, and judge whether there is no such walk in every matrix and then add them together,if the result is 21, it means there are no walks between nodes in every walk matrix, finally I get the number and devided by 2 and get pairs of no walks. The result shows that there are 38 pairs of nodes do not have walks between one another as well.
```{r}
all_network <- simplify(all_network)
all_network_matrix <- as_adjacency_matrix(all_network)
all_network_matrix_2 = all_network_matrix %*% all_network_matrix
all_network_matrix_3 = all_network_matrix_2 %*% all_network_matrix
all_network_matrix_4 = all_network_matrix_3 %*% all_network_matrix
all_network_matrix_5 = all_network_matrix_4 %*% all_network_matrix
all_network_matrix_6 = all_network_matrix_5 %*% all_network_matrix
all_network_matrix_7 = all_network_matrix_6 %*% all_network_matrix
all_network_matrix_8 = all_network_matrix_7 %*% all_network_matrix
all_network_matrix_9 = all_network_matrix_8 %*% all_network_matrix
all_network_matrix_10 = all_network_matrix_9 %*% all_network_matrix
all_network_matrix_11 = all_network_matrix_10 %*% all_network_matrix
all_network_matrix_12 = all_network_matrix_11 %*% all_network_matrix
all_network_matrix_13 = all_network_matrix_12 %*% all_network_matrix
all_network_matrix_14 = all_network_matrix_13 %*% all_network_matrix
all_network_matrix_15 = all_network_matrix_14 %*% all_network_matrix
all_network_matrix_16 = all_network_matrix_15 %*% all_network_matrix
all_network_matrix_17 = all_network_matrix_16 %*% all_network_matrix
all_network_matrix_18 = all_network_matrix_17 %*% all_network_matrix
all_network_matrix_19 = all_network_matrix_18 %*% all_network_matrix
all_network_matrix_20 = all_network_matrix_19 %*% all_network_matrix
all_network_matrix_21 = all_network_matrix_20 %*% all_network_matrix

jud_matrix_1 <- all_network_matrix==0
jud_matrix_2 <- all_network_matrix_2==0
jud_matrix_3 <- all_network_matrix_3==0
jud_matrix_4 <- all_network_matrix_4==0
jud_matrix_5 <- all_network_matrix_5==0
jud_matrix_6 <- all_network_matrix_6==0
jud_matrix_7 <- all_network_matrix_7==0
jud_matrix_8 <- all_network_matrix_8==0
jud_matrix_9 <- all_network_matrix_9==0
jud_matrix_10 <- all_network_matrix_10==0
jud_matrix_11 <- all_network_matrix_11==0
jud_matrix_12 <- all_network_matrix_12==0
jud_matrix_13 <- all_network_matrix_13==0
jud_matrix_14 <- all_network_matrix_14==0
jud_matrix_15 <- all_network_matrix_15==0
jud_matrix_16 <- all_network_matrix_16==0
jud_matrix_17 <- all_network_matrix_17==0
jud_matrix_18 <- all_network_matrix_18==0
jud_matrix_19 <- all_network_matrix_19==0
jud_matrix_20 <- all_network_matrix_20==0
jud_matrix_21 <- all_network_matrix_21==0

sum((jud_matrix_1+jud_matrix_2+jud_matrix_3+jud_matrix_4+jud_matrix_5+
  jud_matrix_6+jud_matrix_7+jud_matrix_8+jud_matrix_9+jud_matrix_10+
  jud_matrix_11+jud_matrix_12+jud_matrix_13+jud_matrix_14+jud_matrix_15+
  jud_matrix_16+jud_matrix_17+jud_matrix_18+jud_matrix_19+jud_matrix_20+jud_matrix_21) == 21)/2
```

# Q5: network-level measure

## (1) Network-level measure of degree centrality = 1
```{r}
st_maxtrix <- matrix(c(0,1,1,1,1,0,0,0,1,0,0,0,1,0,0,0), nrow=4, ncol=4)
st = graph.adjacency(st_maxtrix,'undirected')
plot.igraph(st,vertex.label=NA,layout=layout.fruchterman.reingold,vertex.label.color="black",edge.color="black",vertex.size = 12, edge.arrow.size=.3,edge.curved=FALSE)
st_closeness <- closeness(st) #0.3333333 0.2000000 0.2000000 0.2000000
st_betweenness <- betweenness(st) #3 0 0 0
```
Comment: as we can calculate from the result, this relationship is not true for these networks for closeness centrality and betweenness centrality

## (2)Network-level measure of degree centrality = 0
```{r}
tri_maxtrix <- matrix(c(0,1,1,1,0,1,1,1,0), nrow=3, ncol=3)
tri = graph.adjacency(tri_maxtrix,'undirected')
plot.igraph(tri,vertex.label=NA,layout=layout.fruchterman.reingold,vertex.label.color="black",edge.color="black",vertex.size = 12, edge.arrow.size=.3,edge.curved=FALSE)
tri_closeness <- closeness(tri) #0.5 0.5 0.5
tri_betweenness <- betweenness(tri) #0 0 0
```
Comment: as we can calculate from the result, this relationship hold true for these networks for closeness centrality and betweenness centrality.
