---
title: "HW3_Wei(Will)Jiang"
author: "Wei (Will) Jiang"
date: "11/8/2021"
output: html_document
---
# Set up
```{r, message=FALSE}
library(igraph)
library(data.table)
library(tidyverse)
library(splitstackshape)
library(PearsonDS)
library(plm)
library(pglm)
library(hhi)
border= fread("border_information.csv", header=TRUE)
election= fread("election_results.csv", header=TRUE)
rainfall= fread("monthly_rainfall.csv", header=TRUE)
```

# Data cleaning
```{r,message=FALSE}
#first get the year of each time
rainfall$time <- as.integer(rainfall$time)

#then sum rainfall data when they belongs to a same year and same district
rainfall <- rainfall %>%
  group_by(district,time) %>%
  summarise(rainfall = sum(rainfall))
  
#calculate yearly mean across districts and yearly variance across districts, and then join the average and variance to the rainfall table
rainfall_cal <- rainfall %>%
  group_by(district) %>%
  summarise(rainfall_avg = mean(rainfall),rainfall_var = var(rainfall))

rainfall_norm <- left_join(rainfall,rainfall_cal,by='district')

#in order to use Pearson type III distribution to do pearson transform by using qpearsonIII() function, need calculate rain_norm by using p_norm and use them to calculate scale and shape here for each district-year
#assumption: since the skewness of rainfall is positive, the location parameter c is equal to 0

rainfall_norm$rain_norm <- pnorm(rainfall_norm$rainfall,
                             mean = rainfall_norm$rainfall_avg, 
                             sd = sqrt(rainfall_norm$rainfall_var))

rainfall_norm$scale <- rainfall_norm$rainfall_var / rainfall_norm$rainfall_avg
rainfall_norm$shape <- rainfall_norm$rainfall_avg ** 2 / rainfall_norm$rainfall_var

#use Pearson type III distribution to do pearson transform by using qpearsonIII() function
rainfall_norm$pearson <- qpearsonIII(p = rainfall_norm$rain_norm, 
                                 shape = rainfall_norm$shape, 
                                 location = 0, 
                                 scale = rainfall_norm$scale)

#get SPI(Standardized Precipitation Index) for each district-year : to work with rainfall in a way that is comparable across different regions across time
pearson_cal <- rainfall_norm %>%
  group_by(district) %>%
  summarise(pearson_avg = mean(pearson),pearson_sd = sd(pearson))

rainfall_norm <- left_join(rainfall_norm,pearson_cal,by='district')

rainfall_norm$SPI <- (rainfall_norm$pearson - rainfall_norm$pearson_avg) / rainfall_norm$pearson_sd

#mutate a new column to show if it's a election year or not (yes is 1 and no is 0)
election_time <- unique(election[,'year']) %>%
  mutate(is_election = 1) #find the election time period: each election year

rainfall_norm <- left_join(rainfall_norm,election_time,by=c('time'='year'))
rainfall_norm$is_election <- replace_na(rainfall_norm$is_election,0) #replace NA with 0

```

# Q1

## Q1(A)
```{r,message=FALSE}
#calculate the number of political parties that are founded in a district
election_sub <- election[,c('district','party_name','year','party_issue')]

election_sub <- election_sub %>%
  arrange(district,party_name,year) %>% #reorder
  group_by(district,party_name) %>%
  summarise(time = min(year)) %>% #find the earliest year that a party founded in a district
  group_by(district,time) %>% #find the number of new party in each district-year pair
  summarise(found_num = n()) #group_by %>% summarise(n()) is equal to count()

#filter out time period between earliest and most recent election year and SPI for those year by district
rainfall_Q1 <- rainfall_norm %>%
  select(district,time,is_election,SPI) %>%
  filter(time %in% c(1946:1999))

#join new party data to rainfall data
rainfall_Q1 <- left_join(rainfall_Q1,election_sub,by=c('district','time'))
rainfall_Q1$found_num <- replace_na(rainfall_Q1$found_num,0) #replace NA with 0

#group each year to election year groups
rainfall_Q1 <- rainfall_Q1 %>% mutate(
  election_group = case_when(
  time %in% c(1946:1951) ~ 1,
  time %in% c(1952:1957) ~ 2,
  time %in% c(1958:1962) ~ 3,
  time %in% c(1963:1967) ~ 4,
  time %in% c(1968:1971) ~ 5,
  time %in% c(1972:1977) ~ 6,
  time %in% c(1978:1980) ~ 7,
  time %in% c(1981:1984) ~ 8,
  time %in% c(1985:1985) ~ 9,
  time %in% c(1986:1989) ~ 10,
  time %in% c(1990:1991) ~ 11,
  time %in% c(1992:1996) ~ 12,
  time %in% c(1997:1998) ~ 13,
  time %in% c(1999:1999) ~ 14
)
)

#calculate average SPI in a district across each year from the prior election to the current election
rainfall_Q1_plot <- rainfall_Q1 %>% 
  group_by(district,election_group,.drop = FALSE) %>%
  summarise(SPI_avg = mean(SPI),found_num = sum(found_num))

# plot a scatter plot showing the visual relationship
ggplot(rainfall_Q1_plot, aes(found_num,SPI_avg)) +
  geom_point() +
  labs(x='Number of New Party Founded', y='Average Rainfall SPI')+
  scale_x_continuous(breaks=seq(0,12,by=1))
```

## Q1(B)
```{r,message=FALSE}
#calculate a district and its neighbors' lagged rainfall SPI value

#get a table with both district and its neighbor data, multiple neighbors use average number
rainfall_Q1_border <- rainfall_Q1[,c('district','time','SPI')]
rainfall_Q1_border <- left_join(border,rainfall_Q1_border,by=c('focal_district'='district'))
rainfall_Q1_border <- inner_join(rainfall_Q1_border,rainfall_Q1_border,by=c('district'='focal_district','time'='time'))
rainfall_Q1_border <- distinct(rainfall_Q1_border,focal_district,district,time,SPI.x,SPI.y)
rainfall_Q1_border <- rainfall_Q1_border %>% 
  group_by(focal_district,time) %>%
  summarise(SPI_nb = mean(SPI.y))

rainfall_Q1 <- inner_join(rainfall_Q1,rainfall_Q1_border,by=c('district'='focal_district','time'='time'))

#add a new column to show the number of years in each election period
rainfall_Q1 <- rainfall_Q1 %>% mutate(
  year_num = case_when(
  election_group == 1 ~ (1951-1946+1),
  election_group == 2 ~ (1957-1952+1),
  election_group == 3 ~ (1962-1958+1),
  election_group == 4 ~ (1967-1963+1),
  election_group == 5 ~ (1971-1968+1),
  election_group == 6 ~ (1977-1972+1),
  election_group == 7 ~ (1980-1978+1),
  election_group == 8 ~ (1984-1981+1),
  election_group == 9 ~ (1985-1985+1),
  election_group == 10 ~ (1989-1986+1),
  election_group == 11 ~ (1991-1990+1),
  election_group == 12 ~ (1996-1992+1),
  election_group == 13 ~ (1998-1997+1),
  election_group == 14 ~ (1999-1999+1)
)
)

#group by district-election_group
rainfall_Q1_B <- rainfall_Q1 %>%
  group_by(district,election_group) %>%
  summarise(SPI_avg = mean(SPI),SPI_nb_avg = mean(SPI_nb),year_num = mean(year_num))

#calculate a district's lagged rainfall SPI value and its neighbors' lag SPI by election period
rainfall_Q1_B$SPI_lag <- shift(rainfall_Q1_B$SPI_avg) #lag is not working here so I use shift
rainfall_Q1_B$SPI_nb_lag <- shift(rainfall_Q1_B$SPI_nb_avg)

#run regression between SPI and it's lag SPI & neighbors' lag SPI
plm_lag <- plm(SPI_avg ~ SPI_lag + SPI_nb_lag + year_num, data = rainfall_Q1_B, effect = "twoways", model = "within", index ="district")
summary(plm_lag)
```

Comment: From the regression above, we can see that both SPI_lag and SPI_nb_lag is statistically significant, so the SPI is not independent from one election period to the next within a district, as well as from neighboring districts from one election period to the next.

## Q1(C)
```{r,message=FALSE}
#create a new logical column to see whether its a moderate weather (flood or drought) or not
rainfall_Q1 <- rainfall_Q1 %>%
  mutate(is_moderate = ifelse(SPI < -1 | SPI > 1,1,0),
         is_moderate_nb = ifelse(SPI_nb < -1 | SPI_nb > 1,1,0))

#group by district-election_group
rainfall_Q1_C <- rainfall_Q1 %>%
  group_by(district,election_group) %>%
  summarise(moderate_num = sum(is_moderate),moderate_num_nb = sum(is_moderate_nb),year_num = mean(year_num))

#calculate a district's lagged moderate weather number by election period
rainfall_Q1_C$moderate_num_lag <- shift(rainfall_Q1_C$moderate_num)
rainfall_Q1_C$moderate_num_nb_lag <- shift(rainfall_Q1_C$moderate_num_nb)

#run regression between moderate weather number and it's lag
pglm_lag <- pglm(moderate_num ~ moderate_num_lag + moderate_num_nb_lag + year_num, data = rainfall_Q1_C, effect =
"twoways", model = "within", index = "district", family = "poisson")
summary(pglm_lag)
```

Comment: From the regression above, we can see that both moderate_num_lag and moderate_num_nb_lag is not statistically significant,but year_num is significant. Thus, the result is quite different from the last regression result, which shows that extreme weather in a district and its neighbor districts tends not to influence a districts's next election year's extreme weather.

# Q2

## Q2(A)
```{r,message=FALSE}
#totoal persective: run regression between sum of party founded and number of moderate weather in its own district

rainfall_Q2 <- rainfall_Q1 %>%
  group_by(district,election_group) %>%
  summarise(moderate_sum = sum(is_moderate),moderate_nb_sum = sum(is_moderate_nb),found_sum = sum(found_num),year_num = mean(year_num))

pglm_2A <- pglm(found_sum ~ moderate_sum + year_num, data = rainfall_Q2, effect =
"twoways", model = "within", index = "district", family = "poisson")
summary(pglm_2A)

```

Comment: from the overall perspective, the number of extreme weather has no significant relationship to the number of new political parties founded in a district.

```{r,message=FALSE}
#party issue perspective: run regression by party issue

#thoughts: I have to figure out all the 7 unique party issues first. Then I can filter out their data respectively by using filter(), and then run all the cleaning steps same as above again by using for loop.

party_issue <- unique(election$party_issue)[-1]

#data cleaning by party issue ------------------------------------------------------------------------------------

for (issue in party_issue){

#calculate the number of political parties that are founded in a district
election_lib <- filter(election,party_issue == issue) #filter out data that party issue is liberal
election_lib <- election_lib[,c('district','party_name','year','party_issue')]

election_lib <- election_lib %>%
  arrange(district,party_name,year) %>% #reorder
  group_by(district,party_name) %>%
  summarise(time = min(year)) %>% #find the earliest year that a party founded in a district
  group_by(district,time) %>% #find the number of new party in each district-year pair
  summarise(found_num = n()) #group_by %>% summarise(n()) is equal to count()

#filter out time period between earliest and most recent election year and SPI for those year by district
rainfall_Q1_lib <- rainfall_norm %>%
  select(district,time,is_election,SPI) %>%
  filter(time %in% c(1946:1999))

#join new party data to rainfall data
rainfall_Q1_lib <- left_join(rainfall_Q1_lib,election_lib,by=c('district','time'))
rainfall_Q1_lib$found_num <- replace_na(rainfall_Q1_lib$found_num,0) #replace NA with 0

#group each year to election year groups
rainfall_Q1_lib <- rainfall_Q1_lib %>% mutate(
  election_group = case_when(
  time %in% c(1946:1951) ~ 1,
  time %in% c(1952:1957) ~ 2,
  time %in% c(1958:1962) ~ 3,
  time %in% c(1963:1967) ~ 4,
  time %in% c(1968:1971) ~ 5,
  time %in% c(1972:1977) ~ 6,
  time %in% c(1978:1980) ~ 7,
  time %in% c(1981:1984) ~ 8,
  time %in% c(1985:1985) ~ 9,
  time %in% c(1986:1989) ~ 10,
  time %in% c(1990:1991) ~ 11,
  time %in% c(1992:1996) ~ 12,
  time %in% c(1997:1998) ~ 13,
  time %in% c(1999:1999) ~ 14
)
)

#calculate a district and its neighbors' lagged rainfall SPI value

#get a table with both district and its neighbor data, multiple neighbors use average number
rainfall_Q1_lib_border <- rainfall_Q1_lib[,c('district','time','SPI')]
rainfall_Q1_lib_border <- left_join(border,rainfall_Q1_lib_border,by=c('focal_district'='district'))
rainfall_Q1_lib_border <- inner_join(rainfall_Q1_lib_border,rainfall_Q1_lib_border,by=c('district'='focal_district','time'='time'))
rainfall_Q1_lib_border <- distinct(rainfall_Q1_lib_border,focal_district,district,time,SPI.x,SPI.y)
rainfall_Q1_lib_border <- rainfall_Q1_lib_border %>% 
  group_by(focal_district,time) %>%
  summarise(SPI_nb = mean(SPI.y))

rainfall_Q1_lib <- inner_join(rainfall_Q1_lib,rainfall_Q1_lib_border,by=c('district'='focal_district','time'='time'))

#add a new column to show the number of years in each election period
rainfall_Q1_lib <- rainfall_Q1_lib %>% mutate(
  year_num = case_when(
  election_group == 1 ~ (1951-1946+1),
  election_group == 2 ~ (1957-1952+1),
  election_group == 3 ~ (1962-1958+1),
  election_group == 4 ~ (1967-1963+1),
  election_group == 5 ~ (1971-1968+1),
  election_group == 6 ~ (1977-1972+1),
  election_group == 7 ~ (1980-1978+1),
  election_group == 8 ~ (1984-1981+1),
  election_group == 9 ~ (1985-1985+1),
  election_group == 10 ~ (1989-1986+1),
  election_group == 11 ~ (1991-1990+1),
  election_group == 12 ~ (1996-1992+1),
  election_group == 13 ~ (1998-1997+1),
  election_group == 14 ~ (1999-1999+1)
)
)

#create a new logical column to see whether its a moderate weather (flood or drought) or not
rainfall_Q1_lib <- rainfall_Q1_lib %>%
  mutate(is_moderate = ifelse(SPI < -1 | SPI > 1,1,0),
         is_moderate_nb = ifelse(SPI_nb < -1 | SPI_nb > 1,1,0))

rainfall_Q2_lib <- rainfall_Q1_lib %>%
  group_by(district,election_group) %>%
  summarise(moderate_sum = sum(is_moderate),moderate_nb_sum = sum(is_moderate_nb),found_sum = sum(found_num),year_num = mean(year_num))

pglm_2A_lib <- pglm(found_sum ~ moderate_sum + year_num, data = rainfall_Q2_lib, effect =
"twoways", model = "within", index = "district", family = "poisson")

print(issue)
print(summary(pglm_2A_lib))

}

```

Comment: from the different party issue perspective we can find that parties whose issue is liberal and economic_nonfarming are more likely to be formed when a district experiences extreme weather.

## Q2(B)
```{r}
#create number of moderate weather in a neighbor districts two elections ago
rainfall_Q2 <- rainfall_Q2 %>%
  arrange(district,election_group) %>%
  group_by(district) %>%
  mutate(moderate_nb_sum_lag = shift(moderate_nb_sum))

#run regression between sum of party founded and number of moderate weather in its own district and its neighbor districts two elections ago
pglm_2B <- pglm(found_sum ~ moderate_sum + moderate_nb_sum_lag + year_num, data = rainfall_Q2, effect =
"twoways", model = "within", index = "district", family = "poisson")
summary(pglm_2B)

```

Comment: from the overall perspective, the number of extreme weather in a district and its neighbor has no significant relationship to the number of new political parties founded in a district.

```{r,message=FALSE}
#party issue perspective: run regression by party issue

#thoughts: I have to figure out all the 7 unique party issues first. Then I can filter out their data respectively by using filter(), and then run all the cleaning steps same as above again by using for loop.

party_issue <- unique(election$party_issue)[-1]

#data cleaning by party issue ------------------------------------------------------------------------------------

for (issue in party_issue){

#calculate the number of political parties that are founded in a district
election_lib <- filter(election,party_issue == issue) #filter out data that party issue is liberal
election_lib <- election_lib[,c('district','party_name','year','party_issue')]

election_lib <- election_lib %>%
  arrange(district,party_name,year) %>% #reorder
  group_by(district,party_name) %>%
  summarise(time = min(year)) %>% #find the earliest year that a party founded in a district
  group_by(district,time) %>% #find the number of new party in each district-year pair
  summarise(found_num = n()) #group_by %>% summarise(n()) is equal to count()

#filter out time period between earliest and most recent election year and SPI for those year by district
rainfall_Q1_lib <- rainfall_norm %>%
  select(district,time,is_election,SPI) %>%
  filter(time %in% c(1946:1999))

#join new party data to rainfall data
rainfall_Q1_lib <- left_join(rainfall_Q1_lib,election_lib,by=c('district','time'))
rainfall_Q1_lib$found_num <- replace_na(rainfall_Q1_lib$found_num,0) #replace NA with 0

#group each year to election year groups
rainfall_Q1_lib <- rainfall_Q1_lib %>% mutate(
  election_group = case_when(
  time %in% c(1946:1951) ~ 1,
  time %in% c(1952:1957) ~ 2,
  time %in% c(1958:1962) ~ 3,
  time %in% c(1963:1967) ~ 4,
  time %in% c(1968:1971) ~ 5,
  time %in% c(1972:1977) ~ 6,
  time %in% c(1978:1980) ~ 7,
  time %in% c(1981:1984) ~ 8,
  time %in% c(1985:1985) ~ 9,
  time %in% c(1986:1989) ~ 10,
  time %in% c(1990:1991) ~ 11,
  time %in% c(1992:1996) ~ 12,
  time %in% c(1997:1998) ~ 13,
  time %in% c(1999:1999) ~ 14
)
)

#calculate a district and its neighbors' lagged rainfall SPI value

#get a table with both district and its neighbor data, multiple neighbors use average number
rainfall_Q1_lib_border <- rainfall_Q1_lib[,c('district','time','SPI')]
rainfall_Q1_lib_border <- left_join(border,rainfall_Q1_lib_border,by=c('focal_district'='district'))
rainfall_Q1_lib_border <- inner_join(rainfall_Q1_lib_border,rainfall_Q1_lib_border,by=c('district'='focal_district','time'='time'))
rainfall_Q1_lib_border <- distinct(rainfall_Q1_lib_border,focal_district,district,time,SPI.x,SPI.y)
rainfall_Q1_lib_border <- rainfall_Q1_lib_border %>% 
  group_by(focal_district,time) %>%
  summarise(SPI_nb = mean(SPI.y))

rainfall_Q1_lib <- inner_join(rainfall_Q1_lib,rainfall_Q1_lib_border,by=c('district'='focal_district','time'='time'))

#add a new column to show the number of years in each election period
rainfall_Q1_lib <- rainfall_Q1_lib %>% mutate(
  year_num = case_when(
  election_group == 1 ~ (1951-1946+1),
  election_group == 2 ~ (1957-1952+1),
  election_group == 3 ~ (1962-1958+1),
  election_group == 4 ~ (1967-1963+1),
  election_group == 5 ~ (1971-1968+1),
  election_group == 6 ~ (1977-1972+1),
  election_group == 7 ~ (1980-1978+1),
  election_group == 8 ~ (1984-1981+1),
  election_group == 9 ~ (1985-1985+1),
  election_group == 10 ~ (1989-1986+1),
  election_group == 11 ~ (1991-1990+1),
  election_group == 12 ~ (1996-1992+1),
  election_group == 13 ~ (1998-1997+1),
  election_group == 14 ~ (1999-1999+1)
)
)

#create a new logical column to see whether its a moderate weather (flood or drought) or not
rainfall_Q1_lib <- rainfall_Q1_lib %>%
  mutate(is_moderate = ifelse(SPI < -1 | SPI > 1,1,0),
         is_moderate_nb = ifelse(SPI_nb < -1 | SPI_nb > 1,1,0))

rainfall_Q2_lib <- rainfall_Q1_lib %>%
  group_by(district,election_group) %>%
  summarise(moderate_sum = sum(is_moderate),moderate_nb_sum = sum(is_moderate_nb),found_sum = sum(found_num),year_num = mean(year_num))

#create number of moderate weather in a neighbor districts two elections ago
rainfall_Q2_lib <- rainfall_Q2_lib %>%
  arrange(district,election_group) %>%
  group_by(district) %>%
  mutate(moderate_nb_sum_lag = shift(moderate_nb_sum))

pglm_2A_lib <- pglm(found_sum ~ moderate_sum + moderate_nb_sum_lag + year_num, data = rainfall_Q2_lib, effect =
"twoways", model = "within", index = "district", family = "poisson")

print(issue)
print(summary(pglm_2A_lib))

}
```

Comment: from the different party issue perspective we can find that parties whose issue is liberal, far left, far right, economic_nonfarming and ethnic regional are more likely to be formed when a district's neighbor experiences extreme weather.

# Q3
```{r,message=FALSE}
vote <- select(election,district,year,party_name,vote_count)

#create a new column showing each election group
vote <- vote %>% mutate(
  election_group = case_when(
  year %in% c(1946:1951) ~ 1,
  year %in% c(1952:1957) ~ 2,
  year %in% c(1958:1962) ~ 3,
  year %in% c(1963:1967) ~ 4,
  year %in% c(1968:1971) ~ 5,
  year %in% c(1972:1977) ~ 6,
  year %in% c(1978:1980) ~ 7,
  year %in% c(1981:1984) ~ 8,
  year %in% c(1985:1985) ~ 9,
  year %in% c(1986:1989) ~ 10,
  year %in% c(1990:1991) ~ 11,
  year %in% c(1992:1996) ~ 12,
  year %in% c(1997:1998) ~ 13,
  year %in% c(1999:1999) ~ 14
)
)

#calculate the vote share for each party in each district and each year
vote <- vote %>%
  group_by(district,election_group) %>%
  mutate(vote_sum = sum(vote_count)) %>%
  mutate(vote_share = vote_count / vote_sum)

#calculate HHI(The Herfindahl Index) for each district-election group pair
vote <- vote %>%
  group_by(district,election_group) %>%
  summarise(HHI = sum(vote_share**2))
vote$HHI <- vote$HHI*100

#combine the vote table with HHI information to the table rainfall_Q2
rainfall_Q3 <- left_join(rainfall_Q2,vote,by=c('district','election_group'))

#run regression between sum of party founded and number of moderate weather in its own district and its neighbor districts two elections ago
pglm_3 <- pglm(HHI ~ moderate_sum + moderate_nb_sum_lag + year_num, data = rainfall_Q3, effect =
"twoways", model = "within", index = "district", family = "poisson")
summary(pglm_3)

```

Comment:  the regression illustrates that HHI’s concentration or fragmentation of political power in districts is affected by it's neighbors extreme weather number in that election period.

# Q4
```{r,message=FALSE}

election_sub_Q4 <- election[,c('party_name','district','year')]

#select the founded year of each party in different district 
election_sub_Q4 <- election_sub_Q4 %>%
  arrange(district,party_name,year) %>% #reorder
  group_by(district,party_name) %>%
  summarise(time = min(year))

#election_sub is the count the number of new founded parties in district-election year pair (regardless whether if it's a new party in India)

#find out the earliest time a party is created (new party in India)
election_sub_Q4 <- election_sub_Q4 %>%
  group_by(party_name) %>%
  filter(time == min(time))

election_sub_Q4 <- election_sub_Q4 %>%
  group_by(district,time) %>% #find the number of new party in each district-year pair
  summarise(found_num = n()) #group_by %>% summarise(n()) is equal to count()

#combine the election_sub table and the table above
election_full <- left_join(election_sub,election_sub_Q4,by=c('district','time'))
election_full <- rename(election_full,found_num_dis = found_num.x, found_num_nat = found_num.y)
election_full <- election_full %>%
  mutate(found_diff = found_num_dis - found_num_nat)

#change time in election_full to election group
election_full <- election_full %>% mutate(
  election_group = case_when(
  time %in% c(1946:1951) ~ 1,
  time %in% c(1952:1957) ~ 2,
  time %in% c(1958:1962) ~ 3,
  time %in% c(1963:1967) ~ 4,
  time %in% c(1968:1971) ~ 5,
  time %in% c(1972:1977) ~ 6,
  time %in% c(1978:1980) ~ 7,
  time %in% c(1981:1984) ~ 8,
  time %in% c(1985:1985) ~ 9,
  time %in% c(1986:1989) ~ 10,
  time %in% c(1990:1991) ~ 11,
  time %in% c(1992:1996) ~ 12,
  time %in% c(1997:1998) ~ 13,
  time %in% c(1999:1999) ~ 14
)
)

#combine the two new table to the table rainfall_Q2
rainfall_Q4 <- left_join(rainfall_Q2,election_full,by=c('district','election_group'))

#run regression between sum of party founded (have shown in other districts before) and number of moderate weather in its own district and its neighbor districts two elections ago
pglm_4_A <- pglm(found_num_nat ~ moderate_sum + moderate_nb_sum_lag + year_num, data = rainfall_Q4, effect =
"twoways", model = "within", index = "district", family = "poisson")
print('nationally new party')
print(summary(pglm_4_A))

#run regression between sum of party founded (have not shown in other districts before) and number of moderate weather in its own district and its neighbor districts two elections ago
pglm_4_B <- pglm(found_diff ~ moderate_sum + moderate_nb_sum_lag + year_num, data = rainfall_Q4, effect =
"twoways", model = "within", index = "district", family = "poisson")
print('locally new party')
print(summary(pglm_4_B))

```

Comment: From the regression above, we can find that the number of extreme weather in a district's neighbor have significant influence on both new political parties being founded in a district that have contested an election in a neighboring district in any previous election period and that have not contested an election in a neighboring district in any previous election period.










