---
title: "HW5_Wei(Will)Jiang"
author: "Wei (Will) Jiang"
date: "11/23/2021"
output: html_document
---
# SET UP

```{r,message=FALSE}
library(tidyverse)
library(data.table)
library(lubridate)
library(proxy)
library(hhi)
library(igraph)
library(plm)
library(pglm)
library(plot3D)
library(rgl)
library(plotly)
```

```{r}
company_details <- fread("company_details.csv", header=TRUE)
deal_details <- fread("deal_details.csv", header=TRUE)
investor_details <- fread("investor_details.csv", header=TRUE)
investors_and_deals <- fread("investors_and_deals.csv", header=TRUE)
```


# Q1

## Q1(A)

### Calculate status in each certain years
```{r}
# since we want to make comparisons among firms within the same status hierarchy, only consider in the analysis investors of the Venture Capital type
investor_details <- filter(investor_details,Investor_Type == 'Venture Capital')

# to capture the period of investing where there is a well-defined status hierarchy, consider deals that have occurred from 1990 onward.
deal_details$Deal_Date <- year(dmy(deal_details$Deal_Date))
deal_details <- filter(deal_details,Deal_Date %in% c(1990:2018)) #filter out strange date

# combine all the four tables to one
invest_deals_all <- inner_join(investors_and_deals,deal_details,by=c('Deal_Id' = 'DealId'))
invest_deals_all <- inner_join(invest_deals_all,investor_details,by=c('Investor_Id' = 'InvestorId'))
invest_deals_all <- left_join(invest_deals_all,company_details,by=c('CompanyId' = 'CompanyID'))

rm(investors_and_deals,deal_details,investor_details,company_details)

# calculate status until a certain year below

invest_deals_sub <- invest_deals_all %>% 
  select(1:2,4,10)

invest_bona_cum <- data.frame(status = double(),Investor_Id = character(),Deal_Date = integer())

for (n in 1990:2018){

invest_deals_sub_year <- filter(invest_deals_sub,Deal_Date <= n)

# calculate cumulative proportions between firm pairs until a certain year
invest_deals_prop <- invest_deals_sub_year %>% 
  inner_join(invest_deals_sub_year,by=c('Deal_Id'),suffix=c('_1','_2')) %>% 
  filter(Investor_Id_1 != Investor_Id_2) %>% 
  group_by(Investor_Id_1,Investor_Id_2) %>% 
  mutate(prop = sum(Lead_Investor_1)/n()) %>% 
  select(Investor_Id_1,Investor_Id_2,prop) %>% 
  distinct()

# transfer into network graph and calculate Bonacich centrality
invest_deals_prop_ig <- graph.data.frame(invest_deals_prop,directed = FALSE)

invest_deals_bona <- as.data.frame(power_centrality(invest_deals_prop_ig,exponent = 0.75))
colnames(invest_deals_bona)[1] <- 'status'
invest_deals_bona$Investor_Id <- rownames(invest_deals_bona)
invest_deals_bona$Deal_Date <- n

# combine cumulative Bonacich centrality for each year
invest_bona_cum <- bind_rows(invest_bona_cum,invest_deals_bona)

}

# reset the index and column order
rownames(invest_bona_cum) <- NULL
invest_bona_cum <- invest_bona_cum[,c(2,3,1)]

# combine Bonacich centrality data to the full table
invest_deals_all <- inner_join(invest_deals_all,invest_bona_cum,by=c('Investor_Id','Deal_Date'))

# only consider firms that are actually a part of the status hierarchy, i.e., have co-invested with other firms and have non-missing values for status.
#sum(is.na(invest_deals_all$status)) #see how many NAs
invest_deals_all <- drop_na(invest_deals_all,status)

```


### Calculate HHI to measure cumulative concentration of each venture capital firms' portfolio through each year
```{r,message=FALSE}
# calculate cumulative HHI for each certain year
HHI <- select(invest_deals_all,Investor_Id,Deal_Date,Primary_Industry_Code)

HHI_cum <- data.frame(Investor_Id = character(),Deal_Date = integer(),HHI=double())

for (n in 1990:2018){

HHI_year <- HHI %>% 
  filter(Deal_Date <= n) %>% 
  group_by(Investor_Id) %>% 
  mutate(HHI = as.numeric(hhi(data.frame(c(prop.table(table(Primary_Industry_Code))*100))))) %>% 
  select(-Primary_Industry_Code)

# combine HHI for each year
HHI_year$Deal_Date <- n
HHI_cum <- bind_rows(HHI_cum,HHI_year)
HHI_cum <- distinct(HHI_cum,.keep_all = TRUE)

}

# combine HHI data to the full table
invest_deals_all <- inner_join(invest_deals_all,HHI_cum,by=c('Investor_Id','Deal_Date'))

# save the data so no need to run the for loop again
#save(invest_deals_all, file = "invest_deals_all.RData")
#load("invest_deals_all.RData")

```


### Include lagged control variables like risk exposure and age in the regression
```{r,message=FALSE}
# subset needed data
concen_reg <- select(invest_deals_all,Investor_Id,CompanyId,Deal_Date,status,HHI,Primary_Industry_Sector,Deal_Type_1)

# controls 1: whether a venture capital firm tends to originate its own deals
concen_reg <- concen_reg %>%
  group_by(CompanyId) %>% 
  mutate(is_origin = ifelse(Deal_Date==min(Deal_Date),1,0)) %>% 
  group_by(Investor_Id) %>% 
  mutate(is_originate = ifelse(sum(is_origin)/n() > 0.5,1,0)) %>% 
  select(-is_origin)

# controls 2: whether a venture capital firm tends to invest in the IT sector
concen_reg <- concen_reg %>%
  group_by(CompanyId) %>% 
  mutate(is_IT = ifelse(Primary_Industry_Sector=='Information Technology',1,0)) %>% 
  group_by(Investor_Id) %>% 
  mutate(is_IT = ifelse(sum(is_IT)/n() > 0.5,1,0))

# controls 3: whether a venture capital firm tends to invest in early-stage start-up
concen_reg <- concen_reg %>%
  group_by(CompanyId) %>% 
  mutate(is_early_stage = ifelse(
    Deal_Type_1 %in% c('Early Stage VC','Accelerator/Incubator','Seed Round','Angel (individual)'),1,0)) %>% 
  group_by(Investor_Id) %>% 
  mutate(is_early_stage = ifelse(sum(is_early_stage)/n() > 0.5,1,0))

# group by Investor_Id, Deal_Date
concen_reg <- concen_reg %>% 
  select(-CompanyId,-Primary_Industry_Sector,-Deal_Type_1) %>% 
  distinct()

# controls 4: also include controls for a firm's age and year
age_cal <- deal_details %>% 
  select(DealId, Deal_Date)
age_cal$Deal_Date <- year(dmy(age_cal$Deal_Date))  
age_cal <- filter(age_cal,Deal_Date<2018)

tmp <- investors_and_deals %>% 
  select(Investor_Id, Deal_Id)

age_cal <- inner_join(age_cal,tmp,by=c('DealId'='Deal_Id'))

age_cal <- age_cal %>%
  group_by(Investor_Id) %>% 
  mutate(age = Deal_Date - min(Deal_Date)) %>% 
  arrange(Investor_Id,Deal_Date) %>% 
  select(-DealId) %>% 
  group_by(Deal_Date,Investor_Id) %>% 
  summarise(age = mean(age))

concen_reg <- left_join(concen_reg,age_cal,by=c('Deal_Date','Investor_Id'))
rm(tmp,age_cal)

# create lag for the controls
concen_reg <- concen_reg %>%
  group_by(Investor_Id) %>% 
  mutate(status_lag = dplyr::lag(status), is_originate_lag = dplyr::lag(is_originate), 
         is_IT_lag = dplyr::lag(is_IT), is_early_stage_lag = dplyr::lag(is_early_stage))

```


### Run a regression to explore whetehr higher-status firms are more likely to diversify their investments into different industries than are lower-status firms or middle-status firms.
```{r}
# run regression
concen_reg_out <- plm(HHI ~ status_lag + I(status_lag^2) + is_originate_lag + is_IT_lag + is_early_stage_lag + age + Deal_Date, model = 'within', effect = 'individual', data = concen_reg, index = 'Investor_Id')
summary(concen_reg_out)

```

Comment: From the result above, when we use HHI as a way to measure concentration, status_lag itself is not significant, but status_lag^2 is statistically significant, and it actually have negative effects on concentration(HHI). Therefore, we can know that when a firm' status is low or high, it is less likely for it to diversify its investments into different industries than is a middle-status or middle-status firm.


## Q1(B)

### Take a new measure of diversification as its niche width
```{r,message=FALSE}
invest_cate <- invest_deals_all %>% 
  select(Investor_Id,Deal_Date, Primary_Industry_Code)

invest_cate_jaccard <- data.frame(Primary_Industry_Code=character(),
                                  Primary_Industry_Code_2=character(),
                                  jac_dist=double(),Deal_Date=integer())

for (n in 1990:2018){

#generate affiliation matrix for investor and category in each year
invest_cate_aff_mat <- invest_cate %>%
  filter(Deal_Date <= n) %>% 
  select(Primary_Industry_Code,Investor_Id)
invest_cate_aff_mat <- as.matrix(as.data.frame.matrix(table(invest_cate_aff_mat)))

#calculate Jaccard similarity distance
invest_cate_jac <- dist(invest_cate_aff_mat,method='jaccard',by_rows = TRUE)
invest_cate_jac <- as.matrix(invest_cate_jac) #transfer to distance matrix

jac_dist <- data.table(Primary_Industry_Code=colnames(invest_cate_jac)[col(invest_cate_jac)], Primary_Industry_Code_2=rownames(invest_cate_jac)[row(invest_cate_jac)], jac_dist=c(invest_cate_jac))

jac_dist <- jac_dist %>%
  mutate(Deal_Date = n) 

invest_cate_jaccard <- bind_rows(invest_cate_jaccard,jac_dist)
invest_cate_jaccard <- filter(invest_cate_jaccard,Primary_Industry_Code != Primary_Industry_Code_2)

}

#calculate cumlative number of industries by year and investor id
num_industry = data.frame(Investor_Id = character(),Deal_Date = integer(), num_industry = integer())
for (n in 1990:2018){
  num_industry_n <- invest_cate %>% 
    filter(Deal_Date <= n) %>% 
    group_by(Investor_Id,Deal_Date) %>% 
    summarise(num_industry = length(unique(Primary_Industry_Code)))
  num_industry <- bind_rows(num_industry,num_industry_n)
}
num_industry <- distinct(num_industry)
rm(num_industry_n)

#calculate niche width to measure diversification
invest_cate_result <- invest_cate %>% 
  inner_join(invest_cate,by=c('Investor_Id','Deal_Date'),suffix=c('','_2')) %>% 
  distinct() %>% 
  inner_join(invest_cate_jaccard, by=c('Deal_Date','Primary_Industry_Code','Primary_Industry_Code_2')) %>% 
  left_join(num_industry, by=c('Investor_Id','Deal_Date')) %>% 
  group_by(Investor_Id, Deal_Date) %>% 
  summarise(niche_width = 1 - (1 / (1 + sum(jac_dist) / (num_industry - 1)))) %>% 
  distinct()

#combine the result to the regression data
concen_reg <- concen_reg %>% 
  left_join(invest_cate_result, by=c('Investor_Id','Deal_Date')) %>% 
  left_join(num_industry,by=c('Investor_Id','Deal_Date'))

# change niche width to 0 if number of industry is 1
concen_reg[concen_reg[,'num_industry']==1,'niche_width'] = 0

```


### Include in the model the average values for all of the predictors, except for the year, for each firm over its lifetime
```{r}
# add avearge attributes
concen_reg <- concen_reg %>% 
  group_by(Investor_Id) %>% 
  mutate(status_lag_avg = mean(status_lag, na.rm = TRUE)) %>% 
  mutate(is_originate_lag_avg = mean(is_originate_lag, na.rm = TRUE)) %>% 
  mutate(is_IT_lag_avg = mean(is_IT_lag, na.rm = TRUE)) %>% 
  mutate(is_early_stage_lag_avg = mean(is_early_stage_lag, na.rm = TRUE)) %>% 
  mutate(age_avg = mean(age, na.rm = TRUE))

# change NaN to NA
concen_reg$status_lag_avg[is.nan(concen_reg$status_lag_avg)]<-NA
concen_reg$is_originate_lag_avg[is.nan(concen_reg$is_originate_lag_avg)]<-NA
concen_reg$is_IT_lag_avg[is.nan(concen_reg$is_IT_lag_avg)]<-NA
concen_reg$is_early_stage_lag_avg[is.nan(concen_reg$is_early_stage_lag_avg)]<-NA

```


### Run the same regression as above using the new variable niche width as a new measure of diversification
```{r}
# run regression
concen_reg_out_2 <- glm(niche_width ~ status_lag + I(status_lag^2) + is_originate_lag + is_IT_lag + is_early_stage_lag + age + Deal_Date + status_lag_avg + is_originate_lag_avg + is_IT_lag_avg + is_early_stage_lag_avg + age_avg, family = quasibinomial(link = 'logit'), data = concen_reg)
summary(concen_reg_out_2)

```

Comment: From the result above, when we use niche width as a way to measure concentration, status_lag itself is not significant, but status_lag^2 is statistically significant, and it actually have negative effects on diversification (niche width). Therefore, when we consider how different industry categories might be related, we can know that when a firm' status is low or high, it is less likely for it to diversify its investments into different industries than is a middle-status or middle-status firm.

## Q1(C)

### Check the shape of the regression curve to get a sense of the parabolic curvature
```{r}
# re-run the regression from 1B just using lagged status and the status squared term and not using any of the additional controls and store the result in a object
concen_reg_out_3 <- glm(niche_width ~ status_lag + I(status_lag^2), family = quasibinomial(link = "logit"), data = concen_reg)

# set up a data object with a range of values of the lagged status variable (here set 100 values ranging from the minimum to the maximum)
status_lag_gen = data.frame(status_lag = seq(min(concen_reg$status_lag, na.rm = TRUE), 
                                             max(concen_reg$status_lag, na.rm = TRUE), 
                                             length.out = 100))

# generate fitted values for each of these status values from the regression. Generate 95% confidence intervals for the fitted values by multiplying the standard error of the fit by ±1.96.
status_lag_fit = predict(concen_reg_out_3, newdata = status_lag_gen, se.fit = TRUE)

status_lag_gen$lower = status_lag_fit$fit - 1.96*status_lag_fit$se.fit
status_lag_gen$fit = status_lag_fit$fit
status_lag_gen$upper = status_lag_fit$fit + 1.96*status_lag_fit$se.fit

# Set up a plot with the fitted values and their confidence intervals across the range of lagged status
ggplot(data=status_lag_gen, aes(x=status_lag, y=fit)) +
  geom_line() +
  labs(x='Lag of Status', y='Diversification (Niche Width)', 
       title='Relationship between Lag Status and Diversification (Niche Width)') +
  geom_smooth(aes(ymin = lower, ymax = upper), stat = "identity") +
  theme_light()

```

Comment: from the figure above we can see that the middle-status venture capital firms have more diverse strategies than low-status and high-status venture capital firms.

# Q2

## Q2(A)

### Generate a new attributes: number of successful investments
```{r,message=FALSE}
# generate a count of successful investments venture capital deals that generate cash: a cumulative number of deals for a venture capital firm that fall into the Deal Type 1 categorization “IPO”, “Merger/Acquisition”, or “Buyout/LBO”
success_num <- invest_deals_all %>% 
  select(Investor_Id, Deal_Id, Deal_Date, Deal_Type_1) %>% 
  filter(Deal_Type_1 %in% c('IPO','Merger/Acquisition','Buyout/LBO'))

success_all = data.frame(Investor_Id = character(),suc_num = integer(),Deal_Date = integer())

for (n in 1990:2018){
  success_n <- success_num %>% 
    filter(Deal_Date <= n) %>% 
    group_by(Investor_Id) %>% 
    summarise(suc_num = n()) %>% 
    mutate(Deal_Date = n)
  
  success_all <- bind_rows(success_all,success_n)
}

rm(success_n,success_num)

# combine the new attributes to the regression data table
concen_reg <- left_join(concen_reg,success_all,by=c('Investor_Id','Deal_Date'))

```

### Run regression predicting the number of successful investments as a function of lagged status, lagged diversification, and interaction of lagged status and lagged diversification
```{r}
# generate lag niche_width
concen_reg <- concen_reg %>% 
  group_by(Investor_Id) %>% 
  mutate(niche_width_lag = dplyr::lag(niche_width))

# run regression
concen_reg_out_4 <- pglm(suc_num ~ status_lag + niche_width_lag + status_lag*niche_width_lag + is_originate_lag + is_IT_lag + is_early_stage_lag + age + Deal_Date, model = 'within', effect = 'individual', data = concen_reg, index = 'Investor_Id', family = 'poisson')
summary(concen_reg_out_4)
```

Comment: from the result above, the interaction is not statistically significant so interaction of lagged status
and lagged diversification is not related to having more successful investments.

### Use a 3D visualization to better understand the relationship between the variables in the regression
```{r}
# re-run a similar model from last one with just lagged status and lagged diversification and without using firm fixed effects
concen_reg_out_5 = glm(suc_num ~ status_lag + niche_width_lag + status_lag:niche_width_lag, data = concen_reg, family = "poisson")

# generate a range of combinations of status and diversification
all_value = expand.grid(status_lag=seq(min(concen_reg$status_lag, na.rm = TRUE), 
                                       max(concen_reg$status_lag, na.rm = TRUE), 
                                       length.out = 100), 
                        niche_width_lag=seq(min(concen_reg$niche_width_lag, na.rm = TRUE),
                                            max(concen_reg$niche_width_lag, na.rm = TRUE), 
                                            length.out = 100))

# use predict to get the fitted values for each combination of diversification and status
all_value$suc_num = predict(concen_reg_out_5,newdata=all_value)

# set up plot with x, y, and z variables
scatter3D(all_value$status_lag, all_value$niche_width_lag, all_value$suc_num, phi = 0, bty = "b2", xlab = expression("Lag of Status"), ylab = "Lag of Diversification (Niche Width)", zlab = expression("Number of Successful Investments"), cex.lab = 1, ticktype = "detailed", colkey = list(cex.clab = 1, length = .5, font = 1), clab = c("Predicted values", "of interaction"))

# specify font for below
cmodern = list(family = "CMU Serif", size = 12, color = "black")

# visualization
p1 = plot_ly(
	all_value,
	x = ~status_lag,
	y = ~niche_width_lag,
	z = ~suc_num,
	type = "contour",
	autocontour = FALSE,
	contours = list(
		end = max(all_value$suc_num, na.rm = TRUE),
		size = abs(max(all_value$suc_num,na.rm = TRUE) - min(all_value$suc_num,na.rm = TRUE))/20,
		start = min(all_value$suc_num,na.rm = TRUE),
		showlines = FALSE
		),
	line = list(smoothing = 0.85),

	colorscale = "Greys"
	)

p1 %>% 
  layout(font = cmodern) %>%
  colorbar(len = 1, nticks = 10, title = "Predicted successful \n investments") %>%
  layout(yaxis = list(title = "Lagged niche width")) %>%
  layout(xaxis = list(title = "Lagged status")) 
```

Comment: the patterns suggest about high-status venture capital firms are most successful overall at diversifying their portfolios and low-status venture capital firms are least successful.


# Q3

## Q3(A)

### Use a multidimensional scaling of two dimensions to determine the position of each venture capital firm’s investment portfolio based on its cumulative investments up through each year.
```{r}
#add two coordinates of investors by year as below
invest_deals_sub <- invest_deals_all %>%
  select(Investor_Id, Deal_Date, Primary_Industry_Sector)

coord <- data.frame(Investor_Id=character(),Deal_Date=integer(),coordinate_1=double(),coordinate_2=double())

for (n in 1990:2018){

#generate affiliation matrix

invest_deals_aff_mat <- invest_deals_sub %>%
  filter(Deal_Date <= n)
invest_deals_aff_mat <- invest_deals_aff_mat[,c('Investor_Id','Primary_Industry_Sector')]

invest_deals_aff_mat <- as.matrix(as.data.frame.matrix(table(invest_deals_aff_mat)))

#calculate Jaccard similarity distance regarding Investors and Primary Industry Sector
invest_deals_jac <- dist(invest_deals_aff_mat,method='jaccard',by_rows = TRUE)

#perform the 2D multidimensional scaling
invest_deals_jac <- cmdscale(invest_deals_jac, k=2)

#get coordinate 1 and 2
invest_deals_jac <- cbind(Investor_Id = rownames(invest_deals_jac), invest_deals_jac)
rownames(invest_deals_jac) <- 1:nrow(invest_deals_jac)
invest_deals_jac <- as.data.table(invest_deals_jac)

invest_deals_jac <- invest_deals_jac %>%
  rename(coordinate_1 = V2, coordinate_2 = V3) %>%
  mutate(Deal_Date = n) %>%
  dplyr::select(Investor_Id,Deal_Date,coordinate_1,coordinate_2)

invest_deals_jac$coordinate_1 <- as.double(invest_deals_jac$coordinate_1)
invest_deals_jac$coordinate_2 <- as.double(invest_deals_jac$coordinate_2)

coord <- bind_rows(coord,invest_deals_jac)

}

```


### Define a medoid for each industry category as the coordinates represented by a venture capital firm that only invests in that category in a particular year, use as the medoid the firm with the most investments in this category is no firms invest exclusively in the category
```{r,message=FALSE}
# find how many primary industry sector there is
unique(invest_deals_sub$Primary_Industry_Sector)

# generate a table includes all year and Primary Industry Sector
invest_deals_comb <- invest_deals_sub %>% 
  select(-Investor_Id) %>% 
  distinct %>% 
  arrange(Deal_Date,Primary_Industry_Sector)

# find the investor that invest exclusively in one category each year
invest_deals_exclu <- invest_deals_sub %>%
  group_by(Investor_Id,Deal_Date, Primary_Industry_Sector) %>% 
  mutate(investor_invest_num = n()) %>% 
  filter(investor_invest_num == 1) %>%
  group_by(Investor_Id,Deal_Date) %>% 
  mutate(investor_sector_num = n()) %>% 
  filter(investor_sector_num == 1) %>% 
  select(-investor_invest_num,-investor_sector_num) %>% 
  arrange(Deal_Date,Primary_Industry_Sector)

# get the coordinate of those exclusive investor
invest_deals_exclu <- left_join(invest_deals_exclu,coord,by = c('Investor_Id','Deal_Date'))

# calculate avg as the medoid for that sector in that year
invest_deals_exclu <- invest_deals_exclu %>% 
  group_by(Deal_Date,Primary_Industry_Sector) %>% 
  summarise(medoid_1=mean(coordinate_1),medoid_2=mean(coordinate_2))

# use as the medoid the firm with the most investments in this category is no firms invest exclusively in the category (most then Deal_Date > 1996)
invest_deals_noexclu <- invest_deals_sub %>%
  group_by(Investor_Id,Deal_Date, Primary_Industry_Sector) %>% 
  filter(Deal_Date >= 1996) %>% 
  mutate(investor_invest_num = n()) %>% 
  group_by(Deal_Date,Primary_Industry_Sector) %>% 
  filter(investor_invest_num == max(investor_invest_num)) %>% 
  distinct() %>% 
  arrange(Deal_Date,Primary_Industry_Sector) %>% 
  select(-investor_invest_num)

# get the coordinate of those non-exclusive investor
invest_deals_noexclu <- left_join(invest_deals_noexclu,coord,by = c('Investor_Id','Deal_Date'))

# calculate avg as the medoid for that sector in that year
invest_deals_noexclu <- invest_deals_noexclu %>% 
  group_by(Deal_Date,Primary_Industry_Sector) %>% 
  summarise(medoid_1=mean(coordinate_1),medoid_2=mean(coordinate_2))

# find the year and Primary Industry Sector without exclusive investors
invest_deals_exclu <- filter(invest_deals_exclu,Deal_Date < 1996)
invesr_deals_no_ex <- bind_rows(invest_deals_exclu,invest_deals_noexclu)
invest_deals_comb <- left_join(invest_deals_comb,invesr_deals_no_ex,by=c('Deal_Date','Primary_Industry_Sector'))
rm(invest_deals_exclu,invest_deals_noexclu)

```


### Define the distance between a firm’s experience and the industry category as the Euclidean distance between the firm’s coordinates and the coordinates of the medoid for the industry category
```{r}
# join coordinate and medoid data to one table
invest_deals_sub <- invest_deals_sub %>% 
  left_join(coord, by = c('Investor_Id','Deal_Date')) %>% 
  left_join(invest_deals_comb, by=c('Deal_Date','Primary_Industry_Sector'))

# here we can calculate the Euclidean distance between the firm’s coordinates and the coordinates of the medoid for the industry category

# invest_deals_sub2 <- cbind(c(invest_deals_sub$coordinate_1,invest_deals_sub$coordinate_2),
#                            c(invest_deals_sub$medoid_1,invest_deals_sub$medoid_1))
# 
# invest_deals_euc <- dist(invest_deals_sub2,method='Euclidean',by_rows = TRUE)
# invest_deals_euc <- as.matrix(invest_deals_euc) #transfer to distance matrix
```


### Run regression predicting the average distance between a firm’s syndicate partners and the industry category medoids for the deals that it invests in in a given year, as a function of a firm’s lagged status, the firm’s own average distance from the industry category medoids for the deals that it invests in in a given year, and the interaction between these two variables
```{r}
# before we run regression, we need to calculate avg_dist predicting the average distance between a firm’s syndicate partners and the industry category medoids for the deals that it invests in in a given year

# run regression
concen_reg_out_6 <- plm(avg_dist ~ status_lag + invest_deals_euc + status_lag:invest_deals_euc + is_originate_lag + is_IT_lag + is_early_stage_lag + age + Deal_Date, model = 'within', effect = 'individual', data = investor_dist_year, index = 'Investor_Id')
summary(concen_reg_out_6)
```


### Use a 3D visualization illustrating the relationship between status, a firm’s own distance from the industry categories that it invests in, and the fitted values from the regression
```{r}
# generate a range of combinations of status and diversification
all_value = expand.grid(status_lag=seq(min(concen_reg$status_lag, na.rm = TRUE), 
                                       max(concen_reg$status_lag, na.rm = TRUE), 
                                       length.out = 100), 
                        invest_deals_euc=seq(min(concen_reg$invest_deals_euc, na.rm = TRUE),
                                             max(concen_reg$invest_deals_euc, na.rm = TRUE), 
                                             length.out = 100))

# use the regression model to predict
all_value$avg_dist = predict(concen_reg_out_6,newdata=all_value)

# set up plot with x, y, and z variables
scatter3D(all_value$status_lag, all_value$invest_deals_euc, all_value$avg_dist, phi = 0, bty = "b2", xlab = expression("Lag of Status"), ylab = "Euclidean Distance", zlab = expression("Average Distance"), cex.lab = 1, ticktype = "detailed", colkey = list(cex.clab = 1, length = .5, font = 1), clab = c("Predicted values", "of interaction"))

# specify font for below
cmodern = list(family = "CMU Serif", size = 12, color = "black")

# visualization
p2 = plot_ly(
	all_value,
	x = ~invest_deals_euc,
	y = ~niche_width_lag,
	z = ~avg_dist,
	type = "contour",
	autocontour = FALSE,
	contours = list(
		end = max(all_value$avg_dist, na.rm = TRUE),
		size = abs(max(all_value$avg_dist,na.rm = TRUE) - min(all_value$suc_num,na.rm = TRUE))/20,
		start = min(all_value$avg_dist,na.rm = TRUE),
		showlines = FALSE
		),
	line = list(smoothing = 0.85),

	colorscale = "Greys"
	)

p2 %>% 
  layout(font = cmodern) %>%
  colorbar(len = 1, nticks = 10, title = "Predicted successful \n investments") %>%
  layout(yaxis = list(title = "Lagged niche width")) %>%
  layout(xaxis = list(title = "Lagged status")) 
```



